---
title: "FSB Internship and Full-Time Placement Dashboard 2019-2021"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package initialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT #for better tables
               )

#read in data
intern = readRDS("FSB_BI_Survey_2019_2021.rds")
```

# Survey Overview {data-orientation=columns}

Overview of survey responses
  
## row {data-width=300}

### Internship Rate

```{r, echo = FALSE}

```

### Usable Responses

```{r,echo=FALSE}

# you can find the icons here:https://fontawesome.com/icons
# note that I have been unable to get all icons to work



```   
 
### Overall Major Breakdown
```{r}

```

## row {data-height=600}

### Insights

For this project, we will examine the correlation between internships and full-time placement. More specifically, we will answer the following questions:

1.  If a student has at least one internship, how much more likely are they to have a full-time job than if they did not have an internship?
2.  What if a student has two internships?
3.  Does having an internship mean your salary level will be higher in your full-time job?

From our team's personal experience, we have found that there is immense pressure on students to secure at least one internship during their time at Miami. We are hoping our insights will shed more light on the subject using a data-centric approach.  
   

# 2019 Findings {data-orientation=columns}

## row {data-width=300}

### Usable Responses
```{r}

```

### Accepted Full-Time Offers from Students with at least One Internship
```{r}

```

### Major Breakdown
```{r}

```


## row {data-height=600}

### Post-Grad Plans

```{r,echo=FALSE}

```


### Number of Internships by Major

```{r,echo=FALSE}

```


# 2020 Findings {data-orientation=columns}

## row {data-width=300}

### Usable Responses
```{r}

```

### Accepted Full-Time Offers from Students with at least One Internship
```{r}

```

### Major Breakdown
```{r}

```


## row {data-height=600}

### Post-Grad Plans

```{r,echo=FALSE}

```


### Number of Internships by Major

```{r,echo=FALSE}

```


# 2021 Findings {data-orientation=columns}

## row {data-width=300}

### Usable Responses
```{r}

```

### Accepted Full-Time Offers from Students with at least One Internship
```{r}

```

### Major Breakdown
```{r}

```


## row {data-height=600}

### Post-Grad Plans

```{r,echo=FALSE}

```


### Number of Internships by Major

```{r,echo=FALSE}

```


# Final Findings

### Internship to Full-Time Placement Rate Over Time

```{r}

```

