---
title: "Student Success Project"
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: "Ellie Hoog, Brady Stultz"
output: 
  html_document:
    code_folding: show
    df_print: paged
    number_sections: no
    theme: readable
    toc: yes
    toc_float: yes
    code_download: yes
  word_document:
    toc: no
---

## Audience and Purpose

Our findings will be presented to Kirk Bogard, Associate Vice President for Development and External Relations at FSB. Kirk and his team will use the data and our findings to: 1. Inform FSB rankings 2. Make their case for admission (parents = facts and figures, students = fit and feel) 3. Attract other companies to recruit from FSB 4. Help influence the types of jobs and salary levels they see offered to FSB students 5. FSB Brand Management (sound bites such as: "Farmer students are job ready on Day 1")

Our audience also includes Dr. Allison Jones-Farmer, a shared work practitioner.

## Student Success Business Value Proposition

For this project, we will examine the correlation between internships and full-time placement. More specifically, we will answer the following questions:

1.  If a student has at least one internship, how much more likely are they to have a full-time job than if they did not have an internship?
2.  What if a student has two internships?
3.  Does having an internship mean your salary level will be higher in your full-time job?

From our team's personal experience, we have found that there is immense pressure on students to secure at least one internship during their time at Miami. We are hoping our insights will shed more light on the subject using a data-centric approach.

![](images/StudentSucessBVP.drawio%20(1).png)

## Exploring the Data

```{r}
data = readRDS(file = "FSB_BI_Survey_2019_2021.rds")

head(data)
```

The data source includes three years of data representing FSB graduates, including graduates in 2019, 2020, and 2021. The dataset provided had 42 variables. The source is either derived by me during data cleaning/merging, from the Oracle Business Intelligence Enterprise Edition (OBIEE) maintained by Miami administration, or from the self reported senior survey. The data is a mixture of numeric and categorical variables.

## Data Pre-Processing

Initial drop of variables we feel are unnecessary for our given prompt regarding internships and full-time placement.
```{r}
# Dropping unnecessary variables

data$BBRJ = data$bbrj
data$`Business Direct Admit` = data$BusDirectAdmit
data$`Combined Bacc and Masters` = data$CombBandM
data$`Dean's List`= data$DL
data$`First Generation College Stdnt` = data$FGCS
data$`FSB Scholars` = data$FSBS
data$`Honors Program` = data$HP
data$`President's List` = data$PresList
data$`Study Abroad Courtesy Account` = data$SACA
data$`Transfer Work (Pre-Banner)`= data$TW
data$`Cum Laude` = data$CL
data$`Magna Cum Laude` = data$MCL
data$`Summa Cum Laude` = data$SCL
data$`University Honors` = data$UH
data$`UniversityHonors w/Distinction` = data$UHWD
data$IPEDS.Race.Ethnicity = data$Race
data$Gender = data$Gendergender
data$Term.Code = data$CodeTerm
data$latin_honors = data$honorlatin
data$survey_gradprogram = data$gradpsur
data$survey_gradschool = data$gradssur

```

We're also dropping the following variables: survey_internone, survey_interntwo, survey_internthree, survey_internfour. Most of these values are "N/A". For our analysis, we want to focus on the number of internships, not the company offering the internship.
```{r}
data$survey_internone = data$intern1
data$survey_interntwo = data$intern2
data$survey_internthree = data$intern3
data$survey_internfour = data$intern4
```

We installed the "zoo" package to use the na.fill() function.
```{r}
if (require("zoo")) install.packages("zoo")
pacman::p_load(zoo)

```

Many fields had blank values. In order to work with the data efficiently, we imputed the value "NA" into these fields using na.fill(). 
```{r}
# Impute missing values with "NA"

missing_values = is.na(data)
num_mv = sum(missing_values)
print(num_mv)

data$nmajor = na.fill(data$nmajor, fill = "NA")
data$major1 = na.fill(data$major1, fill = "NA")
data$major2 = na.fill(data$major2, fill = "NA")
data$minor1 = na.fill(data$minor1, fill = "NA")
data$minor2 = na.fill(data$minor2, fill = "NA")
data$GPA.Range = na.fill(data$GPA.Range, fill = "NA")
data$year.x = na.fill(data$year.x, fill = "NA")
data$survey_city = na.fill(data$survey_city, fill = "NA")
data$survey_company = na.fill(data$survey_company, fill = "NA")
data$survey_deptfunc = na.fill(data$survey_deptfunc, fill = "NA")
data$survey_internships = na.fill(data$survey_internships, fill = "NA")
data$survey_offers = na.fill(data$survey_offers, fill = "NA")
data$survey_plans = na.fill(data$survey_plans, fill = "NA")
data$survey_pref_field = na.fill(data$survey_pref_field, fill = "NA")
data$survey_pref_loc = na.fill(data$survey_pref_loc, fill = "NA")
data$survey_salary = na.fill(data$survey_salary, fill = "NA")
data$survey_state = na.fill(data$survey_state, fill = "NA")


```

The variable salary is not imputing with "NA". Rather than assuming a $0 or average salary, we would rather treat these values as null. To fix this, we are going to change the data type from "number" to "character".
```{r}
data$survey_salary = as.character(data$survey_salary)
data$survey_salary = na.fill(data$survey_salary, fill = "NA")
```




## Final Clean Data
```{r}
head(data)
```



## Computing Environment

Our computing environment is an R markdown file within our R project, used in conjunction with GitHub. The R project allows us to bundle our data file and R markdown document to be bundled in its own folder. The GitHub environment enables collaborators to see changes within the documents.